Solving Collective Spin Hamiltonians with Decoherence

### 2018-10-04 soc_squeezing/cumulant_expansions.tex
fixed error in operator product result

We wish to change our basis for all exchange-symmetric operators on a
system of $N$ qubits from $S_+^\ell S_\z^m S_-^n$ to
\begin{align}
  \S_{\v m} \equiv \sum_{\p{\v j;\v m}} P_{\v j},
  &&
  P_{\v j} \equiv \prod_{\mu,a} \sigma_\mu^{\p{j_a^\mu}},
\end{align}
where $\v m \equiv \p{m_\z,m_+,m_-}$; $\v j$ is an ordered list of
indices for the spins addressed by $P_{\v j}$; and the sum over
$\p{\v j;\v m}$ denotes a sum over all possible $\v j$ for which all
indices in $\v j$ are distinct and $\abs{\set{j_a^\mu}} = m_\mu$.  In
words, $\S_{\v m}$ is an exchange-symmetric $\p{m_\z+m_++m_-}$-spin
operator with $m_\mu$ single-spin operators of type $\sigma_\mu$, and
$P_{\v j}$ is a single term in $\S_{\v m}$ which addresses the spins
indexed by $\v j$.

@@

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} f_{\v m\v n\v r}
  \sum_{\p{\v\rho;\v r}} g_{\v\rho} \v\eta_{\v\rho}
  \sum_{\p{\v\ell;\v m,\v n,\v r,\v\rho}}
  c_{\v\ell\v\rho} \S_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where the sums over $\p{\v\rho;\v r}$ and
$\p{\v\ell;\v m,\v n,\v r,\v\rho}$ respectively denote sums over all
values of $\v\rho$ and $\v\ell$ with the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \ell_\mu
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu,
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv \p{ N - \sum_\kappa\ell_\kappa }_{\sum_{\mu,\nu}\rho^{\mu\nu}_0}
\end{align}
accounts for the multiplicity of terms which are equivalent up to a
permutation of indices involving the identity operators in
\eqref{eq:Q_K_rho_simp}.  For clarity, we note here that all indices
on
$m_\mu, n_\mu, r_{\mu\nu}, \rho^{\mu\nu}_\kappa, \eta_{\mu\nu\kappa},
\ell_\mu$ take on the same values as the indices on elements
$\sigma_\mu$ of some complete basis for single-spin operators; of
these, only the last index ($\kappa$) on
$\rho^{\mu\nu}_\kappa,\eta_{\mu\nu\kappa}$ ever matches the index for
the identity element $\sigma_0\equiv\1$.

>>>>

We wish to change our basis for all exchange-symmetric operators on a
system of $N$ spins from $S_+^\ell S_\z^m S_-^n$ to
\begin{align}
  \S_{\v m} \equiv \sum_{\p{\v j;\v m}} P_{\v j},
  &&
  P_{\v j} \equiv \prod_{\mu,a} \sigma_\mu^{\p{j^\mu_a}},
\end{align}
where $\v m \equiv \p{m_\z,m_+,m_-}$ with $m_\mu$ the number of
$\sigma_\mu$ operators in each term of $\S_{\v m}$; $\v j$ is an
ordered list of indices for the spins addressed by $P_{\v j}$; and the
sum over $\p{\v j;\v m}$ denotes a sum over all possible $\v j$ for
which all indices in $\v j$ are distinct and
$\abs{\set{j^\mu_a}} = m_\mu$, such that $j^\mu_a$ indexes the $a$-th
spin addressed by a $\sigma_\mu$ operator in $P_{\v j}$.

@@

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} f_{\v m\v n\v r}
  \sum_{\p{\v\rho;\v r}} g_{\v\rho} \v\eta_{\v\rho}
  c_{\v\ell_{\v m\v n\v r\v\rho}\v\rho} \S_{\v\ell_{\v m\v n\v r\v\rho}},
  \label{eq:SS_simp}
\end{align}
where the sum over $\p{\v\rho;\v r}$ denotes a sum over all
values of $\v\rho$ and with the restrictions
\begin{align}
  \abs{\set{\rho^{\mu\nu}_\kappa}} = \abs{\set{\sigma_\kappa}},
  &&
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu};
\end{align}
the number of $\sigma_\mu$ operators in each term of
$\S_{\v\ell_{\v m\v n\v r\v\rho}}$ is
\begin{align}
  \ell_{\v m\v n\v r\v\rho;\mu}
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu;
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv \p{ N - \sum_\kappa\ell_\kappa }_{\sum_{\mu,\nu}\rho^{\mu\nu}_0}
\end{align}
accounts for the number of terms which are equivalent up to a
permutation of indices involving the identity operators in
\eqref{eq:Q_K_rho_simp}.
